### 2020-01-31 wuhan.tex
push

\section*{Abstract}
A novel coronavirus (2019-nCoV) has recently emerged as a global threat. 
As epidemic progresses, many disease modelers have been prioritized their attention to estimate the basic reproductive number, which is defined as average number of secondary cases caused by a primary case.
While their efforts are extremely valuable, their modeling approaches and, inevitably, their estimates vary widely.

@@

Weakly informative priors are assumed on the hyperparameters:
\begin{linenomath*}
\begin{equation}
\begin{aligned}
\mu_r &\sim \gammdist(\mathrm{mean}=1\,\mathrm{week}^{-1},\,\mathrm{shape}=0.1)\\
\mu_G &\sim \gammdist(\mathrm{mean}=1\,\mathrm{week},\,\mathrm{shape}=0.1)\\
\mu_\kappa &\sim \gammdist(\mathrm{mean}=0.5,\,\mathrm{shape}=0.1)\\
(\alpha_r, \alpha_G, \alpha_\kappa) &\sim \gammdist(\mathrm{mean}=1,\,\mathrm{shape}=0.1).
\end{aligned}
\end{equation}
\end{linenomath*}
We run 4 parallel Markov Chain Monte Carlo (MCMC) chains that consist of 200,000 burnin steps and 200,000 sampling steps.
Posterior samples are thinned every 400 steps.
Convergence is assessed by ensuring that the Gelman-Rubin statistic is below 1.01 for all hyperparameters \citep{gelman1992inference}.
95\% confidence intervals are calculated by taking 2.5\% and 97.5\% quantiles from the posterior distribution.

>>>>

\section*{Abstract}
A novel coronavirus (2019-nCoV) has recently emerged as a global threat. 
As epidemic progresses, many disease modelers have prioritized their attention to estimating the basic reproductive number \Ro, which is defined as the average number of secondary cases caused by a primary case.
While their efforts are extremely valuable, their modeling approaches and, inevitably, their estimates vary widely.
Here, we present a novel framework for comparing different estimates of \Ro\ across a wide range of models by decomposing it into three key quantities (the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$) and apply our framework to arly estimates of \Ro\ for the 2019-nCoV outbreak.
Our results demonstrate the importance of propagating uncertainties in all three quantities, in particular in the mean generation interval.
We recommend that more efforts should be

@@

Weakly informative priors are assumed on the hyperparameters:
\begin{linenomath*}
\begin{equation}
\begin{aligned}
\mu_r &\sim \gammdist(\mathrm{mean}=1\,\mathrm{week}^{-1},\,\mathrm{shape}=0.1)\\
\mu_G &\sim \gammdist(\mathrm{mean}=1\,\mathrm{week},\,\mathrm{shape}=0.1)\\
\mu_\kappa &\sim \gammdist(\mathrm{mean}=0.5,\,\mathrm{shape}=0.1)\\
(\alpha_r, \alpha_G, \alpha_\kappa) &\sim \gammdist(\mathrm{mean}=1,\,\mathrm{shape}=0.1).
\end{aligned}
\end{equation}
\end{linenomath*}
We run 4 parallel Markov Chain Monte Carlo (MCMC) chains that consist of 200,000 burnin steps and 200,000 sampling steps.
Posterior samples are thinned every 400 steps.
Convergence is assessed by ensuring that the Gelman-Rubin statistic is below 1.01 for all hyperparameters \citep{gelman1992inference}.
95\% confidence intervals are calculated by taking 2.5\% and 97.5\% quantiles from the posterior distribution.
\texttt{R} code is available in GitHub (https://github.com/parksw3/nCoV\_framework).
